\plaintitle

### 2017-01-08 drafts/labor/cases.tex
rough pw perspective

{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing,
finding the boundaries of crowd work and microtasks.}
This has largely involved iteratively
  identifying challenges to increasing complexity and
  overcoming them through novel designs of work--flows and processes (e.g.~\cite{bernsteinSoylent,foundry,crowdForgeKittur}).
The question that has emerged then
has been \textit{whether} there are limits to crowdsourcing
--- and if so, what factors determine them.
Through this lens,
a number of contributions to the field have pushed the boundaries of crowd work.

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
First, \namerefl{sec:complexity}.
Second, \namerefl{sec:decomposition}.
And third, \namerefl{sec:relationships}.
We'll explore these aspects of crowdsourcing,  discussing the extents to which work can be
decomposed,  contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
\msb{Our goal will be to use that literature to inform answers to the questions about crowd work (or something like that)}
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

\subfile{complexity.tex}
\subfile{decomposition.tex}
\subfile{relationships.tex}

\onlyinsubfile{
  \printbibliography{}
}

>>>>

{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing,
finding the boundaries of crowd work and microtasks.}
This has largely involved iteratively
identifying barriers on complexity and
overcoming them through novel designs of work--flows and processes (e.g.~\cite{bernsteinSoylent,foundry,crowdForgeKittur}).
The question then
has become \textit{whether} there are limits to crowdsourcing,
and if so, what factors determine them.
To this question, a number of contributions to the field have pressed for answers.

The exploration of on--demand work's potential and limits has principally looked at
manipulating and extending along three dimensions:
First, \namerefl{sec:complexity}.
Second, \namerefl{sec:decomposition}.
And third, \namerefl{sec:relationships}.
We'll explore these aspects of crowdsourcing,  discussing the extents to which work can be
decomposed,  contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
% \msb{Our goal will be to use that literature to inform answers to the questions about crowd work (or something like that)}
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

\notinsubfile{
  \subfile{complexity.tex}
  \subfile{decomposition.tex}
  \subfile{relationships.tex}
}
\onlyinsubfile{
  \printbibliography{}
}

### 2017-01-08 drafts/labor/complexity.tex
rough pw perspective

\subsection[What are the complexity limits of crowd work]
{Identifying the Complexity Limits of Crowd Work}\label{sec:complexity}
A key question to the future of crowd work is
\textit{what} precisely will become part of this economy.
Paid crowdsourcing began with simple microtasks on platforms such as
Amazon Mechanical Turk, but
microtasks are only helpful if they build up to a larger whole.
So, our first question:
how complex can the work outcomes from crowd work be?

@@

\topic{Crowdsourcing research has spent the better part of a decade
proving the viability of crowdsourcing in complex work.}
Unless crowdsourcing can demonstrate viability for meaningfully complex tasks,
the argument runs,
it will be incapable of ensuring a pro--social outcome for work and workers~\cite{crowdworkFuture}.
\citeauthor{crowdForgeKittur} first opened the question of
whether crowdsourcing could be used for goals that are not simple parallel tasks~\cite{crowdForgeKittur}.
Their work demonstrated proof--of--concept crowdsourcing of
a simple encyclopedia article and news summary
--- tasks which could be verified or repeated
with reasonable expectations of similar outcomes.
Seeking to raise the complexity ceiling~\cite{myers2000past},
researchers have since created
additional proof--of--concept applications and techniques,
including conversational assistants~\cite{lasecki2013chorus},
medical data interpreters~\cite{lasecki2013chorus}, and
idea generation work--flows~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
to name a few examples.

\topic{To achieve complex work, this body of research has often applied ideas from Computer Science to design new crowdsourcing workflows.}
Beginning with a goal that has
presented significant challenges for computers,
the researcher leverages an insight from Computer Science
(for example, MapReduce~\cite{crowdForgeKittur} or
sequence alignment algorithms~\cite{lasecki2012real})
and arranges humans as computational black boxes within those approaches.
This approach has proven a compelling one because
it leverages the in--built advantages of
scale,
automation, and
programmability that software affords.

@@

\topic{Finally, the organizational limit on infrastructure creation is somewhat lessened.}
Writing web scripts takes fewer people and fewer hours than creating physical equipment for piecework.
\citeauthor{turkitLittle}'s vision was that any user with basic programming skills could tap into on--demand human intelligence.
As better toolkits lower this threshold~\cite{myers2000past} and computational thinking diffuses, a broader population will be able to use crowd work.

% \clearpage
\subsubsection{\implication}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of crowd work outcomes.
Just as the shift to expert crowdsourcing increased complexity, so too will workers with better tools increase the set of tasks possible.
Beyond this, further improvements would most likely come from replicating the success of narrowly--slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation~\cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework~\cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors~\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more crowd workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to crowd work unless it makes common expertise more broadly available.

Will the shift from human managers to Turing--complete algorithms raise the complexity ceiling? 
By the Turing test, the algorithms would be at best indistinguishable from human piecework clerks and foremen.
So in terms of enabling coordination, algorithmic management is unlikely to directly raise the ceiling beyond what piecework could achieve.
However, as a resource constraint, algorithms are a fixed cost and not a per--person cost like human managers.
So in terms of accessibility, algorithms will allow a broader class of organizations and individuals to afford crowd work.
This shift may enable complex goals that were not cost--effective before to become feasible.
However, because algorithms remain far from replicating all of the foreman's responsibilities,
most likely is a middle ground in which crowd work re--introduces
the human element to management in a more targeted way~(e.g.,~\cite{haas2015argonaut,kulkarni2012mobileworks,crowdguilds}).
This move will require resolving the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest, to break a toxic cycle of mistrustful requesters~\cite{MaliciousCrowdworkersGadiraju}.

Finally, the cost of creating piecework infrastructure has dropped. 
Expensive manufacturing equipment has been largely replaced by computer code~\cite{lessig2006code}.
As with lowered costs of management, lowered infrastructure costs will make crowd work accessible to a broader set of people and organizations.
This in and of itself does not raise the complexity ceiling, but by broadening the potential market for crowd work, it may enable a new set of goals and needs take part.

>>>>

\subsection[What are the complexity limits of on--demand work]
{Identifying the Complexity Limits of On--Demand Work}\label{sec:complexity}
A key question to the future of on--demand work is
\textit{what} precisely will become part of this economy.
Paid crowdsourcing began with simple microtasks on platforms such as
Amazon Mechanical Turk, but
microtasks are only helpful if they build up to a larger whole.
So, our first question:
how complex can the work outcomes from on--demand work be?

@@

\topic{Crowdsourcing research has spent the better part of a decade
proving the viability of crowdsourcing in complex work.}
Unless on--demand work as a whole can demonstrate viability for meaningfully complex tasks,
the argument runs,
it will be incapable of ensuring a pro--social outcome for work and workers~\cite{crowdworkFuture}.
\citeauthor{crowdForgeKittur} first opened the question of
whether crowdsourcing could be used for goals that are not simple parallel tasks~\cite{crowdForgeKittur}.
Their work demonstrated proof--of--concept crowdsourcing of
a simple encyclopedia article and news summary
--- tasks which could be verified or repeated
with reasonable expectations of similar outcomes.
Seeking to raise the complexity ceiling~\cite{myers2000past},
researchers have since created
additional proof--of--concept applications and techniques,
including conversational assistants~\cite{lasecki2013chorus},
medical data interpreters~\cite{lasecki2013chorus}, and
idea generation work--flows~\cite{YuEncouragingOutside,yu2014distributed,Yu2016a},
to name a few examples.

\topic{To achieve complex work, this body of research has often applied ideas from Computer Science to design new crowdsourcing work--flows.}
Beginning with a goal that has
presented significant challenges for computers,
the researcher leverages an insight from Computer Science
(for example, MapReduce~\cite{crowdForgeKittur} or
sequence alignment algorithms~\cite{lasecki2012real})
and arranges humans as computational black boxes within those approaches.
This approach has proven a compelling one because
it leverages the in--built advantages of
scale,
automation, and
programmability that software affords.

@@

\topic{Finally, the organizational limit on infrastructure creation is somewhat lessened.}
Writing web scripts takes fewer people and fewer hours than creating physical equipment for piecework.
\citeauthor{turkitLittle}'s vision was that any user with basic programming skills could tap into on--demand human intelligence.
As better toolkits lower this threshold~\cite{myers2000past} and computational thinking diffuses, a broader population will be able to use on--demand work.

% \clearpage
\subsubsection{\implication}
Technology's ability to support human cognition will enable stronger assumptions about workers' abilities, increasing the complexity of on--demand work outcomes.
Just as the shift to expert crowdsourcing increased complexity, so too will workers with better tools increase the set of tasks possible.
Beyond this, further improvements would most likely come from replicating the success of narrowly--slicing education for expert work as \citeauthor{hart2013rise} and \citeauthor{grier2013computers} described in their piecework examples
of human computation~\cite{grier2013computers} and drastically reformulating macro--tasks given the constraints of piecework~\cite{hart2013rise}.
To some extent, an argument can be made that
MOOCs and other online education resources
provide crowd workers with the resources that they need, but 
it remains to be seen whether that work will be appropriately valued, let alone
properly interpreted by task solicitors~\cite{aguaded2013mooc}.
If we can overcome this obstacle,
we might be able to empower more of these workers to do complex work such as engineering and metalworking,
rather than doom them to ``uneducated'' match girl reputations~\cite{10.2307/3827491}.
However, many such experts are already available on platforms such as Upwork, so training may not directly increase the complexity accessible to on--demand work unless it makes common expertise more broadly available.

Will the shift from human managers to Turing--complete algorithms raise the complexity ceiling? 
By the Turing test, the algorithms would be at best indistinguishable from human piecework clerks and foremen.
So in terms of enabling coordination, algorithmic management is unlikely to directly raise the ceiling beyond what piecework could achieve.
However, as a resource constraint, algorithms are a fixed cost and not a per--person cost like human managers.
So in terms of accessibility, algorithms will allow a broader class of organizations and individuals to benefit from soliciting on--demand work.
This shift may enable complex goals that were not cost--effective before to become feasible.
However, because algorithms remain far from replicating all of the foreman's responsibilities,
most likely is a middle ground in which on--demand work re--introduces
the human element to management in a more targeted way~(e.g.,~\cite{haas2015argonaut,kulkarni2012mobileworks,crowdguilds}).
This move will require resolving the tension between workers and perilously antagonistic managers, as \citeauthor{10.2307/2118435} suggest, to break a toxic cycle of mistrustful requesters~\cite{MaliciousCrowdworkersGadiraju}.

Finally, the cost of creating piecework infrastructure has dropped. 
Expensive manufacturing equipment has been largely replaced by computer code~\cite{lessig2006code}.
As with lowered costs of management, lowered infrastructure costs will make on--demand work accessible to a broader set of people and organizations.
This in and of itself does not raise the complexity ceiling, but by broadening the potential market for on--demand work, it may enable a new set of goals and needs take part.

### 2017-01-08 drafts/labor/conclusion.tex
rough pw perspective

\begin{document}
\section{Conclusion}
Crowd work and on--demand work are not new: they are contemporary instantiations of piecework.
In this paper, we reconsider three major research questions in crowd work using the lens of piecework:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?'';
  \item ``\namerefl{sec:decomposition}?''; and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}
To do so, we draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change change soon.
Reciprocally, we believe that modern crowd work will teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

>>>>

\begin{document}
\section{Conclusion}
On--demand work is not new, but a contemporary instantiations of piecework.
In this paper, we reconsider three major research questions in on--demand work using the lens of piecework:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?'';
  \item ``\namerefl{sec:decomposition}?''; and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}
To do so, we draw on piecework scholarship to inform analyses of what has changed, what hasn't, and may change change soon.
Reciprocally, we believe that modern on--demand work will teach us about the broader phenomenon of piecework as well.
If history really does repeat itself, the best we can do is be prepared.

### 2017-01-08 drafts/labor/decomposition.tex
rough pw perspective

\topic{If decomposition is key to success in crowd work,
the question arises: what can,
and can't,
be decomposed?} 
Moreover,
how thinly can work be sliced and subdivided into smaller and smaller tasks? 
The general trend has been that smaller is better,
and the microtask paradigm has emerged as the overwhelming favorite~\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
This work illustrates a broader sentiment in both the study and practice
of crowd work,
that microtasks should be designed resiliently against the variability of workers,
preventing a single errant submission from impacting the agenda of the work as a whole %,
fully exploiting the abstracted nature of each piece of work
~\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
In this sense,
finer decompositions are seen as more robust
--- both to interruptions and errors~\cite{cheng2015break} ---
even if they incur a fixed time cost.
At the extreme,
recent work has attempted demonstrated
microtasks that take seconds~\cite{Vaish:2014:TCC:2611222.2556996,Cai:2015:WLW:2702123.2702267}
or even fractions of a second~\cite{embracingErrorKrishna}.
However,
workers perform better when similar tasks are strung together~\cite{delayAndOrderLasecki},
or
chained and arranged to maximize the attention threshold of workers~\cite{Cai:2016:CRI:2858036.2858237}.
Despite this,
we as a community have leaned \textit{into} the peril of
low--context work, ``embracing error'' in crowdsourcing~\cite{embracingErrorKrishna}.

@@

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for the better part of a century.}
The beginnings of
systematic task decomposition 
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics,
including
`Arithmetic,
the use of Logarithms,
and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
\begin{Numberlist}
\item work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
\item tasks were discrete
--- that is,
independent from one another.
\item workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.
\end{Numberlist}

@@

Third,
modern crowd work has sliced work to such small scales that the marginal activities
--- things like finding work and cognitive task switching ---
have become large relative to the tasks themselves~\cite{taskSearch}.
In the historical case of piecework,
moving metallurgical tools,
mining equipment,
or
other industry materials would have been prohibitively difficult and slow;
workers were encouraged to specialize in a single set of tasks,
allowing pieceworkers to sequence their tasks optimally on their own~\cite{hart2013rise}.
The result is that crowd workers are more free agents than historically was the case.
However,
because they spend significant time searching for tasks,
the piece rate is less a good estimate of take--home earnings than before.

>>>>

\topic{If decomposition is key to success in on--demand work,
the question arises: what can,
and can't,
be decomposed?} 
Moreover,
how thinly can work be sliced and subdivided into smaller and smaller tasks? 
The general trend has been that smaller is better,
and the microtask paradigm has emerged as the overwhelming favorite~\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
This work illustrates a broader sentiment in both the study and practice
of crowd work,
that microtasks should be designed resiliently against the variability of workers,
preventing a single errant submission from impacting the agenda of the work as a whole %,
fully exploiting the abstracted nature of each piece of work
~\cite{interruptionIqbal,delayAndOrderLasecki,vaish2014low}.
In this sense,
finer decompositions are seen as more robust
--- both to interruptions and errors~\cite{cheng2015break} ---
even if they incur a fixed time cost.
At the extreme,
recent work has attempted demonstrated
microtasks that take seconds~\cite{Vaish:2014:TCC:2611222.2556996,Cai:2015:WLW:2702123.2702267}
or even fractions of a second~\cite{embracingErrorKrishna}.
However,
workers perform better when similar tasks are strung together~\cite{delayAndOrderLasecki},
or
chained and arranged to maximize the attention threshold of workers~\cite{Cai:2016:CRI:2858036.2858237}.
Despite this,
we as a community have leaned \textit{into} the peril of
low--context work, ``embracing error'' in crowdsourcing~\cite{embracingErrorKrishna}.

@@

\topic{The research community relating to
piecework and labor
has been wrestling with the decomposition of work for the better part of a century.}
The beginnings of
systematic task decomposition 
stretch back as far as the \nth{19} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics,
including
`Arithmetic,
the use of Logarithms,
and Elementary Algebra'~''
to compute astronomical phenomena~\cite{grier2013computers}.
The work that Airy solicited resonates with modern crowd work for several reasons.
First, work output was quickly verifiable;
Airy could assign variably skilled workers to compute values,
and have other workers check their work.
Second, tasks were discrete
--- that is,
independent from one another.
Third, workers could be trained on a very narrow subset of mathematical skills to be
sufficiently qualified to do this work.

@@

Third,
modern crowd work has sliced work to such small scales that the marginal activities
--- things like finding work and cognitive task switching ---
have become large relative to the tasks themselves~\cite{taskSearch}.
In the historical case of piecework,
moving metallurgical tools,
mining equipment,
or
other industry materials would have been prohibitively difficult and slow;
workers were encouraged to specialize in a single set of tasks,
allowing pieceworkers to sequence their tasks optimally on their own~\cite{hart2013rise}.
The result is that on--demand workers are more free agents than historically was the case.
However,
because they spend significant time searching for tasks,
the piece rate is less a good estimate of take--home earnings than before.

### 2017-01-08 drafts/labor/discussion.tex
rough pw perspective

\begin{document}
\section{Discussion}
\topic{In our analysis of crowd work via the piecework lens, three issues arose:}
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here explicitly.

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern crowd work.
For example, many of the challenges that \DO~overcame in crowd collective action, such as designing for trustworthiness and ensuring anonymity, were relatively unique challenges precipitated by the affordances of the internet.
For example, unlike physical work environments, people can (and often do) contribute to online communities in a one--off manner
\cite{mcinnis2016one}.
The internet makes this kind of loose affiliation feasible.
While we have attempted to understand the likely overlaps and differences between history and modern day, no analysis is perfect.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

But this does not mean that
attempting to draw meaningfully from historical scholarship would be folly;
enough of piecework can and does inform crowdsourcing that
% we should take this as a cue to look first for
HCI and CSCW might seek out historical framings for other phenomena of study as well.
% as this work can outline both the mechanisms that we should expect to play out
While we can only speculate one of (perhaps many) possible futures, history does allow us to articulate and bound which futures appear more likely.

In particular, the predictions that have emerged surrounding crowd work have run the spectrum
from deep pessimism~\cite{fort2011amazon} to exuberant optimism~\cite{crowdworkFuture}.
In the next section, we will use
the piecework foundation which informed our case studies
to trace out possible dystopian and utopian futures for crowd work.

\subsection{Utopian and Dystopian Visions}\label{sec:polarizationOfCrowdWork}
\topic{An easy narrative is to characterize the future of crowd work  at one of two extremes.}
On one hand, crowd work researchers
imagine the application of crowdsourcing as
a potentially bright future that enables the achievement of near--impossible goals and career opportunities~\cite{redballoon,crowdworkFuture,vizwiz,suzukiAtelier}. % \ali{and who else should I cite here?}
On the other hand, researchers
warn that crowd work will create exploitative sites of dispossession~\cite{scholz2012digital},
racial discrimination~\cite{edelman2015racial},
and invisible, deeply frustrated workers~\cite{turkopticon,bighamHalfWorkday}.

@@

% \topic{There is, of course, a kernel of truth in everything here.}
\topic{Piecework teaches us that, without appropriate norms and policy, the dystopian outcome has happened and will happen again.}
The piecework nature of on--demand work induces us
``to neglect tasks that are less easy to measure'' \cite{SJOE:SJOE371},
rewarding us not for creativity but predictability;
payment for this work may ultimately be determined by
an algorithm that fundamentally doesn't understand people;
the layers between us and our managers might increasingly become
``defective (simple, observable)'' algorithms \cite{10.2307/2555446},
just like those which already frustrate
on--demand workers
\cite{uberAlgorithm,dynamo,turkopticon}.
However, social policy has advanced since the early 1900s, so as crowd work gains popularity a repeat of \textit{How the Other Half Lives}~\cite{riisOtherSideLives} seems less likely.

\topic{On the other hand, while piecework's nascent years were grim, 
they precipitated a century of extremely strong labor advocacy~\cite{hart2013rise,mccallum2013global}.}
Even today, the geist that came out of the labor union revolution
inspires collective action and worker empowerment around the world:
in India, workers across the nation recently engaged in
the largest labor strike in human history
--- perhaps as many as 150 million
\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to permeate on--demand labor markets as some have called for
\cite{futureUnions},
then the future of crowd work may follow
the same trajectory of worker empowerment that piecework \textit{later} found.

@@

% \topic{Perhaps the most pressing question is this:
% is the future of crowd work going to look more \textit{Dystopian} or \textit{Utopian}?}
% If we have learn nothing, crowd work will probably end up somewhere in the middle.
% It's possible that the difficulties of enforcing laws on multinational corporations is
% tipping the balance of power in the direction of corporations, in which case
% things will get worse;
% but arguably we can affect change on the trajectory of crowd work,
% benefiting from everything piecework scholars have learned about
% collective action and governance
% among workers, while also avoiding some of the perils they faced.
% \ali{I really don't like this paragraph, but I felt like we needed to plant a flag on the question in the topic sentence}

\subsection{A Research Agenda}\label{sec:whatShouldBeTheFuture}
Piecework also helps bring into focus the
% Taking a step back from the work that's been done so far and
% thinking about where the body of crowd work research is attempting to go may help us identify
areas of research that might bear the most fruit.
We return to the three questions that motivated this paper:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?''
  \item ``\namerefl{sec:decomposition}?''
        and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}.

While we have arguably outpaced piecework with regard to the limits on the complexity of work,
the most complex and open-ended wicked problems~\cite{rittel1973dilemmas} remain the domain of older human collectives such as governments and organizations. 
% we have yet to find insurmountable limits to crowdsourcing.
In addition, we can learn from the piecework literature as it relates to
the stymieing effect that mismanagement has on workers;
research into the complexity limits should emphasize on finding new ways to manage workers,
in particular using humans --- perhaps other crowd workers ---
to act as modern foremen.

@@

Finally, we turn to the relationships of crowd workers.
The crowd work literature here can convincingly speak back to
the piecework scholarship perhaps more than in the other sections.
The tools that are available to us today
--- not just technical, but \textit{methodological} ---
make it possible to
discover,
study, and
partner with 
% \ali{I feel like Lily would take some umbrage at this because she seemed to not like the narrative of us researchers just unilaterally bequeathing power upon Turkers (well, Turkers certainly disliked it). Thoughts on refactoring?}
crowd workers in ways that were unimaginable to piecework researchers.
A professor engages in crowd work~\cite{bighamHalfWorkday}
not just because it's possible, but because our community
% (of mostly computer scientists)
appreciates the importance of approaches such as participant--observation and ethnography as a whole~\cite{olson2014ways}.
% Whereas piecework didn't have the benefit of Anthropology as we know it or the myriad ways of discovering, learning about, and empowering workers
% What questions are we trying to answer?
% If, as we assumed in
% the previous section on \namerefl{sec:polarizationOfCrowdWork},
% our driving motivation is to empower workers, we

% \end{enumerate}

\endnotetext{
\begin{enumerate}
  \item the past is no guarantee of the future; what could be unforeseen?
  \item it's easy to fall into the (dys|u)--topian camp of what piecework/crowd work will look like
  \item what should we be focusing on? the future of crowd work
\end{enumerate}
}

>>>>

\begin{document}
\section{Discussion}
\topic{In our analysis of on--demand work via the piecework lens, three issues arose:}
\begin{inlinelist}
  \item \namerefl{sec:perilousProblemsPredicting},
  \item \namerefl{sec:polarizationOfCrowdWork}, and
  \item \namerefl{sec:whatShouldBeTheFuture}.
\end{inlinelist}
We will attempt to grapple with these questions here explicitly.

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern on--demand work.
For example, many of the challenges that \DO~overcame in crowd collective action, such as designing for trustworthiness and ensuring anonymity, were relatively unique challenges precipitated by the affordances of the internet.
For example, unlike physical work environments, people can (and often do) contribute to online communities in a one--off manner
\cite{mcinnis2016one}.
The internet makes this kind of loose affiliation feasible.
While we have attempted to understand the likely overlaps and differences between history and modern day, no analysis is perfect.
% articulated in the discussion about
% organizing people and the challenges therein
% \cite{dynamo}, as well as for
% many of the rhizomatic features \citeauthor{miller2011understanding}
% discusses
% \cite{miller2011understanding}).

But this does not mean that
attempting to draw meaningfully from historical scholarship would be folly;
enough of piecework can and does inform on--demand work that
HCI and CSCW might seek out historical framings for other phenomena of study as well.
While we can only speculate one of (perhaps many) possible futures, history does allow us to articulate and bound which futures appear more likely.

In particular, the predictions that have emerged surrounding crowd work have run the spectrum
from deep pessimism~\cite{fort2011amazon} to exuberant optimism~\cite{crowdworkFuture}.
In the next section, we will use
the piecework foundation which informed our case studies
to trace out possible dystopian and utopian futures for on--demand labor.

\subsection{Utopian and Dystopian Visions}\label{sec:polarizationOfCrowdWork}
\topic{An easy narrative is to characterize the future of on--demand labor at one of two extremes.}
On one hand, crowd work researchers
imagine the application of crowdsourcing as
a potentially bright future that enables the achievement of near--impossible goals and career opportunities~\cite{redballoon,crowdworkFuture,vizwiz,suzukiAtelier}.
On the other hand, researchers
warn that on--demand labor will create exploitative sites of dispossession~\cite{scholz2012digital},
racial discrimination~\cite{edelman2015racial},
and invisible, deeply frustrated workers~\cite{turkopticon,bighamHalfWorkday}.

@@

% \topic{There is, of course, a kernel of truth in everything here.}
\topic{Piecework teaches us that, without appropriate norms and policy, the dystopian outcome has happened and will happen again.}
The piecework nature of on--demand work induces us
``to neglect tasks that are less easy to measure'' \cite{SJOE:SJOE371},
rewarding us not for creativity but predictability;
payment for this work may ultimately be determined by
an algorithm that fundamentally doesn't understand people;
the layers between us and our managers might increasingly become
``defective (simple, observable)'' algorithms \cite{10.2307/2555446},
just like those which already frustrate
on--demand workers
\cite{uberAlgorithm,dynamo,turkopticon}.
However, social policy has advanced since the early 1900s, so as on--demand work gains popularity a repeat of \textit{How the Other Half Lives}~\cite{riisOtherSideLives} seems less likely.

\topic{On the other hand, while piecework's nascent years were grim, 
they precipitated a century of extremely strong labor advocacy~\cite{hart2013rise,mccallum2013global}.}
Even today, the geist that came out of the labor union revolution
inspires collective action and worker empowerment around the world:
in India, workers across the nation recently engaged in
the largest labor strike in human history
--- perhaps as many as 150 million
\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to permeate on--demand labor markets as some have called for
\cite{futureUnions},
then the future of on--demand labor may follow
the same trajectory of worker empowerment that piecework \textit{later} found.

@@

\subsection{A Research Agenda}\label{sec:whatShouldBeTheFuture}
Piecework also helps bring into focus the
areas of research that might bear the most fruit.
We return to the three questions that motivated this paper:
\begin{inlinelist}
  \item ``\namerefl{sec:complexity}?''
  \item ``\namerefl{sec:decomposition}?''
        and
  \item ``\namerefl{sec:relationships}?''
\end{inlinelist}.

While we have arguably outpaced piecework with regard to the limits on the complexity of work,
the most complex and open-ended wicked problems~\cite{rittel1973dilemmas} remain the domain of older human collectives such as governments and organizations. 
In addition, we can learn from the piecework literature as it relates to
the stymieing effect that mismanagement has on workers;
research into the complexity limits should emphasize on finding new ways to manage workers,
in particular using humans --- perhaps other crowd workers ---
to act as modern foremen.

@@

Finally, we turn to the relationships of crowd workers.
The crowd work literature here can convincingly speak back to
the piecework scholarship perhaps more than in the other sections.
The tools that are available to us today
--- not just technical, but \textit{methodological} ---
make it possible to
discover,
study, and
partner with 
crowd workers in ways that were unimaginable to piecework researchers.
A professor engages in crowd work~\cite{bighamHalfWorkday}
not just because it's possible, but because our community
appreciates the importance of approaches such as participant--observation and ethnography as a whole~\cite{olson2014ways}.
